---
title: "ridgereg"
author: "Carolina Rosário and Elisio Quintino"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ridgereg}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
# Predictive modeling with Ridgereg
Let's do some analysis regarding predictive modeling. The dataset BostonHousing will be used in this demonstration.

```{r setup}
library(lab4elife599carde734)
library(caret)
library(mlbench)
library(leaps)


```

First, we need to divide the BostonHousing data into a test and training dataset.
```{r}
data("BostonHousing")

set.seed(123)
trainIndex <- createDataPartition(BostonHousing$medv, p = .8, 
                                  list = FALSE, 
                                  times = 1)

BostonTrain <- BostonHousing[ trainIndex,]
BostonTest  <- BostonHousing[-trainIndex,]

head(BostonTrain)
head(BostonTest)
```
Fit a linear regression model
```{r}
lm_model <- train(medv ~ .,
               data = BostonTrain,
               method = "lm")

```
Fit a linear regression model with forward selection of covariates
```{r}
forward_selection  <- train(medv ~ ., data  =  BostonTrain ,
                             method  =  "leapForward" )

```
Now we want to evaluate the perfomance of the models that we have just created. To do that, we need to calculate the RMSE (the lower the better) and R-squared (the bigger the better). Both RMSE and R-squared quantify how well a regression model fits a dataset. The RMSE tells us how well a regression model can predict the value of the response variable in absolute terms while R-squared tells us how well a model can predict the value of the response variable in percentage terms
```{r}

trainX  <-  BostonTrain[,-(which(names(BostonTrain)=="medv"))]
trainY  <-  BostonTrain$medv


testX  <-  BostonTest[,-(which(names(BostonTest)=="medv"))]
testY  <-  BostonTest$medv

predictions_lm <- predict(lm_model, BostonTest)
predictions_forward <- predict(forward_selection, BostonTest)


#RMSE - The lower the better

lm_model_rmse<- RMSE(predictions_lm,testY)
lm_forward_rmse<- RMSE(predictions_forward,testY)

#R2 (R-squared) - The higher the better

lm_model_r2<- R2(predictions_lm,testY)
lm_forward_r2<- R2(predictions_forward,testY)

#RMSE for Linear Regression
print(lm_model_rmse)

#RMSE for Linear Regression forward selection
print(lm_forward_rmse)

#R2 for Linear Regression
print(lm_model_r2)

#R2 for Linear Regression forward selection
print(lm_forward_r2)

#For both indicator, linear regression model seems to be the model that predicts better the data

```
